
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                   Coipcheart                                            %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\chapter*{C\'oipcheart} 
\addcontentsline{toc}{chapter}{C\'oipcheart}

\begin{center}
\textit{Permission is granted to copy, distribute and/or \\
modify this document under the terms of the \\
\href{http://www.gnu.org/copyleft/fdl.html}{GNU Free Documentation License}, \\
Version 1.2 or any later version published by the \\
\href{http://www.gnu.org/fsf/fsf.html}{Free Software Foundation}; \\
with no Invariant Sections, no Front-Cover Texts, \\
and no Back-Cover Texts. \\
A copy of the license is included in the section entitled \\
``GNU Free Documentation License''.}
\vspace{7ex}

An Ch\'ead Eagr\'an \copyright \hspace{0.6ex} Ean\'air 2007 \\
\vspace{1ex}
An tEagr\'an seo 
\copyright \hspace{0.6ex} Caoimh\'{\i}n P. \'O Scanaill \the\year \\
\vspace{20ex}
{\small Arna chl\'ochur le \LaTeX}
\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                   Giorruchain                                           %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\chapter*{Giorr\'uch\'ain} 
\addcontentsline{toc}{chapter}{Giorr\'uch\'ain}
\begin{tabbing}
\hspace*{35ex}\=\hspace{25ex}\=\kill
\> {\it aid, a1, a2, a3} \> aidiacht \\
\> {\it af} \> ainmfhocal \\
\> {\it b} \> baininscneach \\
\> {\it b2, b3, \ldots} \> ainmfhocal baininscneach \\
\> {\it br, br1, br2} \> briathar \\
\> {\it db} \> dobhriathar \\
\> {\it f} \> firinscneach \\
\> {\it f1, f3, \ldots} \> ainmfhocal firinscneach \\
\> {\it iol} \> iolra \\
\end{tabbing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                   Usaid                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{{\'U}s\'aid} 
\addcontentsline{toc}{chapter}{\'Us\'aid}

\begin{itemize}
\item There are about 1000 {\em primary entries} given in {\bf boldface}
and followed by lists of related nouns, verbs, adjectives, and
adverbs, respectively.  
\vspace{2ex}
\item The remaining entries are given in plain type and are followed by 
hypertext cross-references (in {\bf boldface}) to one or more primary entries.
\vspace{2ex}
\item Entries are in strict alphabetical order without regard for
spaces, hyphens, or apostrophes.
\vspace{2ex}
\item No variant spellings or detailed grammatical information is given.
\vspace{2ex}
\item Bibliographical references are provided for words not
appearing in the standard references: 
{\it Focl\'oir Gaeilge-B\'earla} \cite{OD77} agus
an {\it English-Irish Dictionary} \cite{Ba59}.
\vspace{2ex}
\item For reasons of space, we have not been systematic about including 
verbal nouns, 
past participles, genitives used attributively, adverbs formed from
``go'', etc.  The savvy Gaeilgeoir should be able to deal with this.
\vspace{2ex}
\item More ideas from thesaurii?
\end{itemize}
\endinput
